---
title: "Population Structure"
author: "Ira Cooke"
output: github_document
---

```{r, echo=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8,
                      echo=FALSE, warning=FALSE, message=FALSE)
```

We used PCAngst to infer population structure from low whole genome sequencing data on our 20 *P. speciosa* samples.  PCAngst creates a sample covariance matrix to allow model-free genetic clustering of samples. It also calculates the optimal number of clusters and calculates admixture proportions based on these. 

As input data to PCAngst we used bam files produced by following the GATK best practices workflow for mapping reads to the host genome, as well as marking adapters and duplicats. `angsd` was then used to call variant sites and calculate genotype likelihoods at all of those sites. See [hpc/angsd/02_import_vcf.sh] for full details.

Genotype likelihood values were then used as input to `PCAngst` to produce a covariance matrix. 

```{r}
library(tidyverse)
library(ggpubr)

cluster_colors <- c("Cluster3" = "#e41a1c","Cluster2" = "#377eb8", "Cluster1" = "#4daf4a")

samples <- read_tsv("hpc/angsd/all.bamlist",col_names = "bam") %>% 
  pull(bam) %>% 
  stringr::str_extract(pattern = "DC([^\\_]+)")
  
sample_data <- read_tsv("raw_data/samples.txt") %>% 
  filter(SampleCode!="") %>% 
  select(Sample=SampleCode,Pop=Cluster,Location,PimSC) %>% 
  add_row(Pop="Cluster1",Location="Unknown",Sample="DCRM31")
  
sample_data <- sample_data[match(samples,sample_data$Sample),]
```


```{r}
covmat <- read_table2("hpc/angsd/pcangst3.cov",col_names = FALSE) %>% 
  as.matrix()

colnames(covmat) <- sample_data$Sample
rownames(covmat) <- sample_data$Sample

pop_eigen <- eigen(covmat)

pop_pca <- data.frame(x=pop_eigen$vectors[,1],y=pop_eigen$vectors[,2],sample_data) %>% 
  mutate(Location = str_remove(Location,"GBR - ")) %>% 
  filter(Location!="Unknown")

ggplot(pop_pca ,aes(x=x,y=y)) + geom_point(aes(shape=Location,color=Pop),size=2) + 
  theme_pubclean() +
  guides(color='none') +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  xlab("PC1") + ylab("PC2") +
  scale_color_manual(values = cluster_colors)

ggsave("figures/PCAngst.png")
```

Admixture proportions are also calculated by PCAngst (based on optimal K = 3).  These can be plotted in the style of a STRUCTURE plot as follows;

```{r}
library(RcppCNPy)
sample_ids <- sample_data$Sample

# Cluster1 : Green
# Cluster3 : Red
# Cluster2 : Blue

#cluster_names <- c("Cluster1"="X1","Cluster2"="X2","Cluster3"="X3")
cluster_order <- c("Cluster1"=2,"Cluster2"=1,"Cluster3"=3)

q3_m <- npyLoad("hpc/angsd/pcangst3.admix.Q.npy")
colnames(q3_m) <- c("qG","qR","qB")

q3_admix <- q3_m %>% as_tibble() %>% 
  add_column(Sample = sample_ids) %>% 
  gather(cluster,proportion,-Sample) %>% 
  left_join(sample_data) %>% 
  mutate(pop_order = cluster_order[Pop])


accols <- cluster_colors
names(accols) <- c("qR","qB","qG")

ggplot(q3_admix %>% filter(Sample!="DCRM31") ,aes(x=reorder(PimSC,desc(pop_order)),y=proportion)) + 
  geom_bar(aes(fill=cluster),color="black",stat="identity") + 
  theme_minimal() + 
  xlab("") + ylab("Admixture Proportion") + 
  scale_color_manual(values = accols) +
  scale_fill_manual(values = accols, labels = names(cluster_colors)) + 
  theme(axis.text.x = element_text(angle=90), legend.title = element_blank(), legend.position = 'None') +
  theme(line = element_blank()) + coord_flip() + theme(axis.text.x = element_blank()) +
  guides(color=FALSE)

ggsave("figures/PCAngst_Admix.png",width = 4, height = 7)
```

