---
title: "Whole Genome Sequencing Coverage Summary"
output: github_document
---


```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8,
                      echo=FALSE, warning=FALSE, message=FALSE)
```

The table below shows sequencing coverage estimates for all 20 samples used for whole genome sequencing. Values are estimates from `samtools depth` based on scaffold `Sc0000001`.  Samples used for MSMC analysis are indicated with a `*`.

Sample ID | Location | Coverage | Lineage  | MSMC 
--------- | ------- | -------- | --------- | -----
DC1104	| GBR - Myrmidon BackReef |	4.45 | Green | 
DC1107	| GBR - Myrmidon BackReef	| 23.1 | Blue | *
DC1108	| GBR - Myrmidon BackReef	| 15.2 | Blue | *
DC1105	| GBR - Myrmidon BackReef	| 21.1 | Red | *
DC1109	| GBR - Myrmidon BackReef	| 28.0 | Red | *
DC7967	| GBR - GreatDet BackReef	| 24.2 | Green | *
DC7969	| GBR - GreatDet BackReef	| 22.3 | Green | *
DC7962	| GBR - GreatDet BackReef	| 27.8 | Blue | *
DC7968	| GBR - GreatDet BackReef	| 26.6 | Blue | *
DC7955	| GBR - GreatDet BackReef	| 26.6 | Red | *
DC7957	| GBR - GreatDet BackReef	| 28.9 | Red | *
DC7958	| GBR - GreatDet BackReef	| 8.6 | Red |
DC8218	| GBR - Ribbon10 BackReef	| 6.1 | Green |
DC8230	| GBR - Ribbon10 BackReef	| 6.5 | Green |
DC8235	| GBR - Ribbon10 BackReef	| 6.5 | Green |
DC8220	| GBR - Ribbon10 BackReef	| 5.0 | Blue |
DC8229	| GBR - Ribbon10 BackReef	| 5.6 | Blue |
DC8222	| GBR - Ribbon10 BackReef	| 4.0 | Blue |
DC8223	| GBR - Ribbon10 BackReef	| 4.4 | Red |
DC8238	| GBR - Ribbon10 BackReef	| 4.6 | Red |





```{r}
library(tidyverse)
```